### 2018-09-08 pilot_manuscript.Rmd
Fixed comma issues, etc.

#Fair
fair_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA"])]

@@

#Ingroup
ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA"])]

@@

#Authority
authority_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA"])]

@@

#Purity
purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA"])]

>>>>

#Fair
fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)

fair_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]

@@

#Ingroup
ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)

ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & !is.na(ingroup_all$words)]), ]

@@

#Authority
authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)

authority_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA" & !is.na(authority_all$words)]), ]

@@

#Purity
purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)

purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA" & !is.na(purity_all$words)]), ]
